EldersAIR: demographics summary

### 2020-03-13 demographics_summary.Rmd
summary stat updates

---
title: "EldersAIR: demographics summary"
author: "Ethan Walker"
date: "Started 6 March 2020, Updated 12 March 2020"
output: pdf_document
---

@@

## For Winter 1, there were 145 homes with demographic data (76 NN and 69 NP)
## and 150 participants with demographic data (79 NN and 71 NP)
## 5 homes had 2 participants (3 NN and 2 NP); all other homes had 1 participant

@@

demographics_function(demographics_filtered, "gender", "Participant sex", "count")
demographics_function(demographics_filtered, "hispanic", "Hispanic ethnicity", "count")
demographics_function(demographics_filtered, "race", "Participant race", "count")
demographics_function(demographics_filtered, "income", "Household income", "count")
demographics_function(demographics_filtered, "education", "Participant education", "count")
demographics_function(demographics_filtered, "total_residents", "Total residents", "count")
demographics_function(demographics_filtered, "residents_under18", "Residents under 18", "count")
```

>>>>

---
title: "EldersAIR: demographics summary"
author: "Ethan Walker"
date: "Started 6 March 2020, Updated 12 March 2020"
output: powerpoint_presentation
---

@@

For Winter 1, there were 145 homes with demographic data (76 NN and 69 NP)
and 150 participants with demographic data (79 NN and 71 NP)
5 homes had 2 participants (3 NN and 2 NP); all other homes had 1 participant

@@

```

```{r}
demographics_function(demographics_filtered, "gender", "Participant sex", "count")
```

```{r}
demographics_function(demographics_filtered, "hispanic", "Hispanic ethnicity", "count")
```

```{r}
demographics_function(demographics_filtered, "race", "Participant race", "count")
```

```{r}
demographics_function(demographics_filtered, "income", "Household income", "count")
```

```{r}
demographics_function(demographics_filtered, "education", "Participant education", "count")
```

```{r}
demographics_function(demographics_filtered, "total_residents", "Total residents", "count")
```

```{r}
demographics_function(demographics_filtered, "residents_under18", "Residents under 18", "count")
```
